### 2020-04-28 README.Rmd
added race
pm2.5 for us added

The other datsets were obtained from the [Homeland Infrastructure Foundation](https://hifld-geoplatform.opendata.arcgis.com/datasets/hospitals/data?page=18), the [Census](https://data.census.gov/cedsci/table?q=United%20States), [Mapping Medicare Disparities](https://data.cms.gov/mapping-medicare-disparities), and [activity indexes](https://github.com/COVIDExposureIndices/COVIDExposureIndices) calculated by  Victor Couture, Jonathan Dingel, Allison Green, Jessie Handbury, and Kevin Williams based on smartphone movement data provided by `PlaceIQ`.

@@

* `act_ind`: county-level device exposure index (DEX), an index of activity.
* `acm_househ`: several metric regarding household composition (2018).
* `age_sex`: age and sex distribution (2018).
* `fl65`:  percentage of fee-for-service (FFS) Medicare enrollees that had an annual flu vaccination (2017)
* `hospbeds`: total hospital beds in each county (2019).
* `mmd`: data of 2017 regarding the  prevalence found in medicare beneficiaries of 
    * many medical and chronic conditions (Alzheimer, chronic kidney, obesity, depression, obstructive pulmonary, disease, arthritis, diabetes, osteoporosis, asthma, atrial  fibrillation, ischemic hearth, myocardial infarction, hypertension).
    * several type of cancer.
    * emergency,  medical admissions and annual visits.
    * pneumoccocal vaccine.
    * tobacco use.

>>>>

The other datsets were obtained from the [Homeland Infrastructure Foundation](https://hifld-geoplatform.opendata.arcgis.com/datasets/hospitals/data?page=18), the [Census](https://data.census.gov/cedsci/table?q=United%20States), [Mapping Medicare Disparities](https://data.cms.gov/mapping-medicare-disparities), and [activity indexes](https://github.com/COVIDExposureIndices/COVIDExposureIndices) calculated by  Victor Couture, Jonathan Dingel, Allison Green, Jessie Handbury, and Kevin Williams based on smartphone movement data provided by `PlaceIQ`. Emissions of pm2.5 in micro g/m3 (2016) were reported by \href{http://fizz.phys.dal.ca/~atmos/martin/?page_id=140#V4.NA.02.MAPLE}{Atmoshpheric Composition Analysis Group} and
#'  aggregate by \href{https://github.com/wxwx1993/PM_COVID/blob/master/additional_preprocessing_code/download_pm25_values.md}{Ista Zahn and Ben Sabath}

@@

* `act_ind_us`: county-level device exposure index (DEX), an index of activity.
* `acm_househ_us`: several metric regarding household composition, including poverty, education, ancestry (2018).
* `age_sex_us`: age and sex distribution (2018).
* `race_us`: estimated races in population (2018).
* `fl65_us`:  percentage of fee-for-service (FFS) Medicare enrollees that had an annual flu vaccination (2017)
* `hospbeds_us`: total hospital beds in each county (2019).
* `mmd_us`: data of 2017 regarding the  prevalence found in medicare beneficiaries of 
    * many medical and chronic conditions (Alzheimer, chronic kidney, obesity, depression, obstructive pulmonary, disease, arthritis, diabetes, osteoporosis, asthma, atrial  fibrillation, ischemic hearth, myocardial infarction, hypertension).
    * several type of cancer.
    * emergency,  medical admissions and annual visits.
    * pneumoccocal vaccine.
    * tobacco use.
* `pm2.5_us`: Emissions of pm2.5 in micro g/m3
